DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/introduction.tex
removed more svn stuff from the documentation, explained to use candi for thirdparty deal.II libries

\begin{enumerate}[A)]
\item You can obtain a copy of \dope{} from the developers svn repository using\\
\texttt{svn co --username=[your username] \textbackslash \\ 
\hspace*{5mm}https://svn.dopelib.net/dope}\\
(The backslash in the first line means that the line will be continued as one!)

Note that you need a valid username and password. If you have none, please contact the 
maintainers by sending an EMail to \url{dope@dopelib.net}.
%
\item You can download the sources as a tar-ball from the project website\\ 
\url{http://www.dopelib.net}.
\end{enumerate}

@@

We would like to express our gratitude to the former maintainer
\begin{itemize}
\item Christian Goll (Maintainer from 2009--2015)
\end{itemize}

@@

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install \ 
      -DDEAL_II_WITH_UMFPACK=true \
      -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags

\begin{lstlisting}
-DDEAL_II_WITH_TRILINOS=true -DTRILINOS_DIR=[path to trilinos]
\end{lstlisting}

for the use of MPI use

\begin{lstlisting}
-DDEAL_II_WITH_MPI=true
\end{lstlisting}

and for the use of distributed meshes over several computers the p4est
library is needed in deal.II to use this use the flags (in addition to the use of MPI)
\begin{lstlisting}
-DDEAL_II_WITH_P4EST=true -DP4EST_DIR=[path to p4est]
\end{lstlisting}

>>>>

\begin{enumerate}[A)]
\item You can obtain a copy of \dope{} from the developers git repository using\\
\texttt{git clone git://git.mathematik.tu-darmstadt.de/dopelib} \\
in the command line of your terminal.

%Note that you need a valid username and password. If you have none, please contact the 
%maintainers by sending an EMail to \url{dope@dopelib.net}.
%
\item You can download the sources as a tar-ball from the project website\\ 
\url{http://www.dopelib.net}.
\end{enumerate}

@@

We would like to express our gratitude to the former maintainer
\begin{itemize}
\item Christian Goll (Maintainer from 2009--2015)
\end{itemize}
%%% TODO: add Daniel Jodlbauer and Bernhard Endtmayer

@@

\begin{remark}
Our current DOpE installation has been successfully tested for deal.II version 8.5.0.
\end{remark}

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
cd build 
cmake -DCMAKE_INSTALL_PREFIX=/path/to/install/dir ../deal.II
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to
cmake. An excellent description is provided on the deal.II webpage
\begin{lstlisting}
http://www.dealii.org/8.5.0/readme.html
\end{lstlisting}

\subsection{deal.II ThirdPartyLibraties}
To install third party libraries used for deal.II we recommend to use
the candi script:
\begin{lstlisting}
https://github.com/koecher/candi
\end{lstlisting}
On this webpage, you will find also enough information how to use 
the candi script.
